The Astropy Project

### 2017-12-10 main.tex
typos

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
we show an RGB color image of the Hickson 88 group, centered near
NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}
This image was generated from SDSS images using the
\package{astropy.visualization} tools.

>>>>

The Sloan Digital Sky Survey (SDSS) SkyServer color images were made using a
variation on this technique.  As an example, in \figurename~\ref{fig:ngc6977},
we show an RGB color image of the Hickson 88 group, centered near
NGC~6977.\footnote{\url{http://skyserver.sdss.org/dr13/en/tools/chart/navi.aspx?ra=313.12381&dec=-5.74611}}
This image was generated from SDSS images using the
\package{astropy.visualization} tools.
